Computing exact restricted isometry constants via\\ mixed integer semidefinite programming

### 2016-03-10 RIP-MISDP-Paper/IEEE_RIP-MISDP.tex
corrected order of d'Aspremont citations

However, one drawback of the RIP is that computing the restricted isometry
constants for a given matrix~$A$ and~$k$ is NP-hard, see~\cite{PT14}. On
the other hand, d'Aspremont et al.~\cite{Asp07,Asp08} proposed several
semidefinite relaxations to compute upper bounds on the restricted isometry
constants. Note that small upper bounds suffice to guarantee
$\ell_0$-$\ell_1$-equivalence between~\eqref{l0min} and~\eqref{l1min}, but
there exist cases in which the bounds are too weak to give a guarantee.

The relaxations in \cite{Asp07,Asp08} were originally derived for the deeply
connected problem of sparse principal component analysis (SPCA). Principal
component analysis (PCA) is about finding orthogonal directions maximizing the 
variance given in matrix $A$. SPCA tries to fix the problem that the components
of PCA usually consist of small contributions of all axes, which make the results
hard to interpret, by enforcing sparsity on the components. SPCA was
originally proposed by Zuo et al. in \cite{SPCA}, where a penalty term was added 
to the objective. Other authors like Moghaddam et al. in \cite{sbSPCA} also proposed 
computing a sparse maximal eigenvalue for SPCA, like it is done for the RIP.

>>>>

However, one drawback of the RIP is that computing the restricted isometry
constants for a given matrix~$A$ and~$k$ is NP-hard, see~\cite{PT14}. On
the other hand, d'Aspremont et al.~\cite{Asp08,Asp07} proposed several
semidefinite relaxations to compute upper bounds on the restricted isometry
constants. Note that small upper bounds suffice to guarantee
$\ell_0$-$\ell_1$-equivalence between~\eqref{l0min} and~\eqref{l1min}, but
there exist cases in which the bounds are too weak to give a guarantee.

The relaxations in \cite{Asp08,Asp07} were originally derived for the deeply
connected problem of sparse principal component analysis (SPCA). Principal
component analysis (PCA) is about finding orthogonal directions maximizing the 
variance given in matrix $A$. SPCA tries to fix the problem that the components
of PCA usually consist of small contributions of all axes, which make the results
hard to interpret, by enforcing sparsity on the components. SPCA was
originally proposed by Zuo et al. in \cite{SPCA}, where a penalty term was added 
to the objective. Other authors like Moghaddam et al. in \cite{sbSPCA} also proposed 
computing a sparse maximal eigenvalue for SPCA, like it is done for the RIP.
